\textbf{Evaluating RISC-V Enclaves:}\\ Security Without the Slowdown?

### 2025-09-05 draft_presentation.tex
added new diagrams

% What is RISC-V? Slide
\begin{frame}{What is RISC-V?}
\begin{itemize}
    \item Open-source, modular processor architecture.
    \item Highly customizable for specialized hardware (ideal for enclaves).
    \item Scalable from embedded systems to high-performance computing.
    \item Growing adoption in academia and industry (e.g., SiFive, Western Digital).
\end{itemize}
\begin{block}{Key Concept}
\textit{RISC-V’s open-source nature enables flexible, secure processor designs for enclave-based systems.}
\end{block}
\end{frame}

>>>>

% What is RISC-V? Slide
\begin{frame}{What is RISC-V?}
\begin{itemize}
    \item Open-source, modular processor architecture.
    \item Highly customizable for specialized hardware (ideal for enclaves).
    \item Scalable from embedded systems to high-performance computing.
    \item Growing adoption in academia and industry (e.g., SiFive, Western Digital).
\end{itemize}
% \begin{block}{Key Concept}
% \textit{RISC-V’s open-source nature enables flexible, secure processor designs for enclave-based systems.}
% \end{block}

\begin{center}
\scalebox{1}{ % adjust this factor to shrink or enlarge
\begin{tikzpicture}[font=\scriptsize, >=latex, node distance=0.5cm]

% Base ISA
\node[draw, fill=blue!20, thick, minimum width=5cm, minimum height=0.8cm, align=center] (isa) {\textbf{RISC-V ISA} \\ Open, stable foundation};

% Optional Extensions layer
\node[draw, fill=yellow!30, thick, minimum width=4.5cm, minimum height=0.8cm, align=center, above=of isa] (ext) {Optional Extensions \\ (Vector, Crypto, Custom...)};

% Application domains
\node[draw, fill=orange!30, thick, rounded corners, minimum width=2.8cm, minimum height=0.8cm, align=center, above left=0.9cm and 0.4cm of ext] (embedded) {Embedded};
\node[draw, fill=green!30, thick, rounded corners, minimum width=2.8cm, minimum height=0.8cm, align=center, above=0.9cm of ext] (hpc) {HPC};
\node[draw, fill=purple!30, thick, rounded corners, minimum width=2.8cm, minimum height=0.8cm, align=center, above right=0.9cm and 0.4cm of ext] (enclave) {Enclaves};

% Arrows
\draw[->, thick] (isa) -- (ext);
\draw[->, thick] (ext.north west) .. controls +(0,0.4) and +(0,-0.4) .. (embedded.south);
\draw[->, thick] (ext.north) -- (hpc.south);
\draw[->, thick] (ext.north east) .. controls +(0,0.4) and +(0,-0.4) .. (enclave.south);

\end{tikzpicture}
} % end scalebox
\end{center}
\end{frame}
